Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-03-11 Paper/Manuscript_Stats&Comp/manuscript_STCO.tex
quick look for undefined references

As commented in next Section~\ref{sec_diagnostic_criticism}, the estimated $\hat{\ell}$ being larger than diagnostic threshold doesn't guarantee that the approximate is sufficiently accurate, and thus we recommend to look at the predicitve accuracy measures, too.

@@

The developed approximate GPs can be easily applied as modular components in probabilistic programming frameworks such as Stan in both Gaussian and non-Gaussian observation models. Using several simulated and real datasets, we have demonstrated the practical applicability and improved sampling efficiency, as compared to exact GPs, of the developed method. The main drawback of the approach is that its computational complexity scales exponentially with the number of input dimensions. Hence, choosing optimal values for the number of basis functions and the boundary factor, using the recommendations and diagnostics provided in Figures~\ref{fig6_7_relationships} and \ref{fig6_7_relationships}, is essential to avoid a excessive computational time especially in multivariate input spaces. However, in practice, input dimensionalities larger than three start to be computationally demanding even for moderately wiggly functions and few basis functions per input dimension. In these high dimensional cases, the proposed approximate GP methods may still be used for low-dimensional components in an additive modeling scheme but without modeling very high dimensional interactions, as complexity is linear with the number of additive components.

>>>>

As commented above, the estimated $\hat{\ell}$ being larger than diagnostic threshold doesn't guarantee that the approximate is sufficiently accurate, and thus we recommend to look at the predicitve accuracy measures, too.

@@

The developed approximate GPs can be easily applied as modular components in probabilistic programming frameworks such as Stan in both Gaussian and non-Gaussian observation models. Using several simulated and real datasets, we have demonstrated the practical applicability and improved sampling efficiency, as compared to exact GPs, of the developed method. The main drawback of the approach is that its computational complexity scales exponentially with the number of input dimensions. Hence, choosing optimal values for the number of basis functions and the boundary factor, using the recommendations and diagnostics provided in Figure~\ref{fig6_relationships}, is essential to avoid a excessive computational time especially in multivariate input spaces. However, in practice, input dimensionalities larger than three start to be computationally demanding even for moderately wiggly functions and few basis functions per input dimension. In these high dimensional cases, the proposed approximate GP methods may still be used for low-dimensional components in an additive modeling scheme but without modeling very high dimensional interactions, as complexity is linear with the number of additive components.
